\huge Tor's Usability for Censorship Circumvention

### 2016-04-06 pets2017-paper/pets2017-paper.tex
\mbox email address to prevent line breaking.
It looked bad (and was ambiguous) to have lines broken like:

David Fifield: University of California Berkeley, E-mail: fi-
field@eecs.berkeley.edu

Serge Egelman: University of California Berkeley
and International Computer Science Institute, E-mail: egel-
man@cs.berkeley.edu

  \affil[1]{University of Caifornia Berkeley, E-mail: lnl@cs.berkeley.edu}

  \affil[2]{University of Caifornia Berkeley, E-mail: fifield@eecs.berkeley.edu}

  \affil[3]{University of Caifornia Berkeley, E-mail: nmalkin@cs.berkeley.edu}

  \affil[4]{University of Caifornia Berkeley, E-mail: ganesh.v@berkeley.edu}

  \affil[5]{University of Caifornia Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}

  \affil[6]{University of Caifornia Berkeley, E-mail: daw@cs.berkeley.edu}

>>>>

  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@eecs.berkeley.edu}}

  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}

  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}

  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}

  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
